---
title: "TITLE <br><span style = 'font-size: 80%;'>  "
author: " <span style = 'font-size: 120%; line-height: 1.8'>Tiago Ventura </strong>, Co-Author 1, Co-Author 2 </span>"
date: " <span style = 'font-size: 100%;'> <br> Conference, MM/DD/YYYY </span>"
output:
  xaringan::moon_reader:
    includes:
      in_header: "no_favicon.html"
    css: ["xaringan-themer.css", "custom.css", "mytheme-fonts.css"]
    lib_dir: libs
    self_contained: false
    nature:
      #ratio: 16:9
      #ratio: 191:100
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "Slide %current% of %total%"
---
layout: true
<div class="my-footer"><span>Tiago Ventura (Georgetown University) &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp &nbsp Conference YYYY</span></div>
```{r setup, include=FALSE}
library(xaringanthemer)
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message=FALSE, warning = FALSE)
xaringanthemer::style_mono_light(base_color ="#23395b",
                                  title_slide_text_color="#ffff",
                                  title_slide_background_color = "#23395b",
                                  background_color = "#fff",
                                  link_color =  "#C93312")
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, error=TRUE, echo=FALSE, cache=TRUE)
```

```{r style-share-again, echo=FALSE}
xaringanExtra::use_tile_view()
xaringanExtra::use_panelset()
```


---
class: middle

## Motivation

<!-- Add motivation content here -->

--

<!-- Add bullet points here -->

---
class: middle

## Research Questions

- **RQ1:**

- **RQ2:**

---
class: middle

# Design and Methods

--

<!-- Add methods content here -->

---
class: middle, center, inverse

# Results

---
class: middle, center

## Result 1

<!-- Add figure or content -->

---
class: middle, center

## Result 2

<!-- Add figure or content -->

---
class: middle

## Conclusion

<!-- Add conclusion content here -->

--

<!-- Add bullet points here -->

---
class: middle, inverse, center

# Thank you!
